Structural Divergence Analysis

### 2017-04-23 analysis-structure.Rmd
bibliografíapaper, varios r0 y dinámica

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
sim.data.no.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))

```

@@

```{r read-functional-sites}
# which are the functional sites?
functional.sites = read.csv(functional.sites.fname, sep = ";")
active.site.index = functional.sites$index
description = functional.sites$description
function.info = data.frame(active.site.index, description)
```

In this case we studied the `r family` family. 
We used the ENM `r enm` with R0 = `r R0` to generate mutants.
We used as reference for the ENM the protein with pdb code `r reference`. 
The active/functional sites of the reference are:

@@

cor.df = data.frame("comparison" = c("exp vs mut", "exp vs medium", "mut vs medium"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

```{r comparisons-between-plots}

@@

plot(x = d.exp$mean.z.RSD, 
     y = d.mut$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "mut.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
abline(0, 1)

plot(x = d.exp$mean.z.RSD, 
     y = d.medium$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "medium.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.medium$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.medium$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)

plot(x = d.mut$mean.z.RSD, 
     y = d.medium$mean.z.RSD, 
     xlab = "mut.mean.z.RSD", 
     ylab = "medium.mean.z.RSD", 
     xlim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))),
     ylim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))))
points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.medium$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.medium$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)
```

@@

# comparison of means.z.scores with the minimum distance to the functional sites
plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CA, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")

## calculate correlations between profiles
r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CA)
r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM)

cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))

@@

# comparison of means.z.scores with the sum.inv distance to the functional sites
plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.sum.inv.da.CM.CA$sum.inv.da.CA, xlab = "sum.inv distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.sum.inv.da.CM.CA$sum.inv.da.CM, xlab = "sum.inv distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")

## calculate correlations between profiles
r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.sum.inv.da.CM.CA$sum.inv.da.CA)
r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.sum.inv.da.CM.CA$sum.inv.da.CM)

cor.df = data.frame("comparison" = c("(exp - mut) vs sum.inv.da.CA", "(exp - mut) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))

@@

```{r correlation-da-CN} 
## calculate correlations between profiles
r.min.da.CA.CN = cor(CN, m.min.da.CM.CA$min.da.CA)
r.min.da.CM.CN = cor(CN, m.min.da.CM.CA$min.da.CM)

@@

## calculate correlations between profiles
r.sum.inv.da.CA.CN = cor(CN, m.sum.inv.da.CM.CA$sum.inv.da.CA)
r.sum.inv.da.CM.CN = cor(CN, m.sum.inv.da.CM.CA$sum.inv.da.CM)

@@

In this section we compare theoretical sequence profiles with sequence scores obtained from ConsurfDB. To obtain theoretical profiles, we calculated the number of times we had mutated each site for each selection regimen.

@@

# read simulated data
## no sel
sim.data.no.sel = read.csv(sim.data.no.sel.fname)
mut.site.no.sel = sim.data.no.sel$site
p.accept.no.sel = sim.data.no.sel$p.accept

## medium sel
sim.data.medium.sel = read.csv(sim.data.medium.sel.fname)
mut.site.medium.sel = sim.data.medium.sel$site
p.accept.medium.sel = sim.data.medium.sel$p.accept

# calculate mean.p.accept of simulated data
mean.p.accept.no.sel = c()
mean.p.accept.medium.sel = c()

# correct indexes
if (data.dir == "OUT/out_subset_CM_ANM") {
  mut.site.no.sel = mut.site.no.sel - n.sites
  mut.site.medium.sel = mut.site.medium.sel - n.sites
  CN.CM = sim.data.no.sel$CN
  CN = c()

  for (i in (1:n.sites)) {
    CN[i] = CN.CM[which(mut.site.no.sel == i)][1]
  }
}

for (i in (1:n.sites)) {
  p.accept.no.sel.i = p.accept.no.sel[which(mut.site.no.sel == i)]
  mean.p.accept.no.sel.i = mean(p.accept.no.sel.i)
  mean.p.accept.no.sel[i] = mean.p.accept.no.sel.i

  p.accept.medium.sel.i = p.accept.medium.sel[which(mut.site.medium.sel == i)]
  mean.p.accept.medium.sel.i = mean(p.accept.medium.sel.i)
  mean.p.accept.medium.sel[i] = mean.p.accept.medium.sel.i
}

@@

plot(x = mean.p.accept.no.sel, y = CN)
plot(x = mean.p.accept.no.sel, y = score)
plot(x = score, y = CN)

## calculate corelations
r.mean.p.accept.no.sel.CN = cor(mean.p.accept.no.sel, CN)
r.mean.p.accept.no.sel.score = cor(mean.p.accept.no.sel, score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison" = c("p.accept.no.sel vs CN", "p.accept.no.sel vs score", "score vs CN"),
                    "R" = c(r.mean.p.accept.no.sel.CN , r.mean.p.accept.no.sel.score, r.score.CN))

@@

@@

plot(x = log(mean.p.accept.medium.sel), y = CN)
plot(x = log(mean.p.accept.medium.sel), y = score)
plot(x = score, y = CN)

## calculate corelations
r.mean.p.accept.medium.sel.CN = cor(log(mean.p.accept.medium.sel), CN)
r.mean.p.accept.medium.sel.score = cor(log(mean.p.accept.medium.sel), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison" = c("log(p.accept.medium.sel) vs CN", "log(p.accept.medium.sel) vs score", "score vs CN"),
                    "R" = c(r.mean.p.accept.medium.sel.CN , r.mean.p.accept.medium.sel.score, r.score.CN))

@@

```

@@

plot(x = d.exp$mean.z.RSD, y = CN, xlab = "experimental <zRSDi>")
plot(x = d.mut$mean.z.RSD, y = CN, xlab = "theoretical with no selection <zRSDi>")
plot(x = d.medium$mean.z.RSD, y = CN, xlab = "theoretical with medium selection <zRSDi>")

## calculate corelations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN)
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, CN)
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, CN)

cor.df = data.frame("comparison" = c("exp.mean.z.RSD vs CN", "mut.mean.z.RSD vs CN", "medium.mean.z.RSD vs CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation structure - sequence")
```

>>>>

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
```

@@

```{r read-functional-sites}
# which are the functional sites?
functional.sites = read.csv(functional.sites.fname, sep = ";")
active.site.index = functional.sites$index
description = functional.sites$description
function.info = data.frame(active.site.index, description)
```
In this case we studied the `r family` family. 
We used the ENM `r enm` with R0 = `r R0` to generate mutants.
We used as reference for the ENM the protein with pdb code `r reference`. 
The active/functional sites of the reference are:

@@

cor.df = data.frame("comparison" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

```{r comparisons-between-profiles}

@@

plot(x = d.exp$mean.z.RSD, 
     y = d.mut$mean.z.RSD, 
     xlab = "<z.RSD> experimental", 
     ylab = "<z.RSD> no-selection", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
abline(0, 1)

plot(x = d.exp$mean.z.RSD, 
     y = d.medium$mean.z.RSD, 
     xlab = "<z.RSD> experimental", 
     ylab = "<z.RSD> selection", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.medium$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.medium$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)

plot(x = d.mut$mean.z.RSD, 
     y = d.medium$mean.z.RSD, 
     xlab = "<z.RSD> no-selection", 
     ylab = "<z.RSD> selection", 
     xlim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))),
     ylim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))))
points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.medium$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.medium$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)
```

@@

# comparison of means.z.scores with the minimum distance to the functional sites
plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], x = m.min.da.CM.CA$min.da.CA[-active.site.index], xlab = "minimal distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], x = m.min.da.CM.CA$min.da.CM[-active.site.index], xlab = "minimal distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")

## calculate correlations between profiles
r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], m.min.da.CM.CA$min.da.CA[-active.site.index])
r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], m.min.da.CM.CA$min.da.CM[-active.site.index])

cor.df = data.frame("comparison" = c("(exp - no-selection) vs min.da.CA", "(exp - no-selection) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))

knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")

# comparison of means.z.scores with the minimum distance to the functional sites
plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], x = m.min.da.CM.CA$min.da.CA[-active.site.index], xlab = "minimal distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], x = m.min.da.CM.CA$min.da.CM[-active.site.index], xlab = "minimal distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> selection")

## calculate correlations between profiles
r.min.da.CA = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], m.min.da.CM.CA$min.da.CA[-active.site.index])
r.min.da.CM = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], m.min.da.CM.CA$min.da.CM[-active.site.index])

cor.df = data.frame("comparison" = c("(exp - selection) vs min.da.CA", "(exp - selection) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))

@@

# comparison of means.z.scores with the sum.inv distance to the functional sites
plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], x = m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index], xlab = "sum.inv distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], x = m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index], xlab = "sum.inv distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")

## calculate correlations between profiles
r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index])
r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index])

cor.df = data.frame("comparison" = c("(exp - no-selection) vs sum.inv.da.CA", "(exp - no-selection) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))

knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the sum.inv distance to the active site")

# comparison of means.z.scores with the sum.inv distance to the functional sites
plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], x = m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index], xlab = "sum.inv distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], x = m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index], xlab = "sum.inv distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> selection")

## calculate correlations between profiles
r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index])
r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index])

cor.df = data.frame("comparison" = c("(exp - selection) vs sum.inv.da.CA", "(exp - selection) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))

@@

```{r correlation-da-CN} 
## calculate correlations between profiles
r.min.da.CA.CN = cor(CN[-active.site.index], m.min.da.CM.CA$min.da.CA[-active.site.index])
r.min.da.CM.CN = cor(CN[-active.site.index], m.min.da.CM.CA$min.da.CM[-active.site.index])

@@

## calculate correlations between profiles
r.sum.inv.da.CA.CN = cor(CN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index])
r.sum.inv.da.CM.CN = cor(CN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index])

@@

In this section we compare theoretical sequence divergence profiles with sequence scores obtained from ConsurfDB. To obtain theoretical profiles, for each selection regimen, we calculated the number of times we had mutated each site and divided this number by the number of times we had tried a mutation at the site.

@@

# read simulated data
## no sel
sim.data.mut = read.csv(sim.data.mut.fname)
mut.site.mut = sim.data.mut$site
accept.mut = sim.data.mut$accept

## medium sel
sim.data.medium.sel = read.csv(sim.data.medium.sel.fname)
mut.site.medium.sel = sim.data.medium.sel$site
accept.medium.sel = sim.data.medium.sel$accept

# calculate p.accept of simulated data
p.accept.mut = c()
p.accept.medium.sel = c()

# correct indexes
if (data.dir == "OUT/out_subset_CM_ANM") {
  mut.site.mut = mut.site.mut - n.sites
  mut.site.medium.sel = mut.site.medium.sel - n.sites
  CN.CM = sim.data.mut$CN
  CN = c()

  for (i in (1:n.sites)) {
    CN[i] = CN.CM[which(mut.site.mut == i)][1]
  }
}

for (i in (1:n.sites)) {
  accept.mut.i = accept.mut[which(mut.site.mut == i)]
  p.accept.mut.i = mean(accept.mut.i)
  p.accept.mut[i] = p.accept.mut.i

  accept.medium.sel.i = accept.medium.sel[which(mut.site.medium.sel == i)]
  p.accept.medium.sel.i = mean(accept.medium.sel.i)
  p.accept.medium.sel[i] = p.accept.medium.sel.i
}

@@

plot(x = log(p.accept.mut), y = CN, xlab = "log(paccept no-selection)")
plot(x = log(p.accept.mut), y = score, xlab = "log(paccept no-selection)")
plot(x = score, y = CN)

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, CN)
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

print("<paccept no-selection>")
print(mean(p.accept.mut))

@@

plot(x = log(p.accept.medium.sel), y = CN, xlab = "log(paccept selection)")
plot(x = log(p.accept.medium.sel), y = score, xlab = "log(paccept selection)")
plot(x = score, y = CN)

## calculate corelations
r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

print("<paccept selection>")
print(mean(p.accept.medium.sel))
```

@@

plot(x = d.exp$mean.z.RSD, y = CN, xlab = "<zRSDi> experimental ")
plot(x = d.mut$mean.z.RSD, y = CN, xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = CN, xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN)
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, CN)
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, CN)

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
```
